Interval Probability for Fuzzy Quantum Theories

### 2016-06-23 prob.tex
prob.tex Before meeting...

\begin{definition}[Quantum Probability
Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\tensor*[_{[0,1]}]{\mu}{} : \events \rightarrow [0,1]$ such
  that:\footnote {It is possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item $\tensor*[_{[0,1]}]{\mu}{}(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $P_{i}$, we have 
$\tensor*[_{[0,1]}]{\mu}{}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\tensor*[_{[0,1]}]{\mu}{}\left(P_{i}\right)$.
\end{itemize}
Notice that the preposing $[0,1]$ indicates the range of
$\tensor*[_{[0,1]}]{\mu}{}$. We will only prepose the range of a
probability measure whenever we need to compare the ranges of different
probability measures later. 
\qed\end{definition}

@@

\begin{lemma}\label{lem:quantumProbabilityMeasure}Given a Hilbert
space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$ is a probability
measure if and only if $\mu$ satisfies the following conditions:
\begin{itemize}
\item $\mu(\mathbb{0})=0$, 
\item $\mu(\mathbb{1})=1$, 
\item for any projection $P$,
$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, and 
\item for a set of mutually orthogonal projections $P_{i}$, we have
$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$.
\end{itemize}
\qed\end{lemma}

@@

\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$,
for any function~$\mu:\events\rightarrow[0,1]$ satisfies the conditions
listed in lemma~\ref{lem:quantumProbabilityMeasure}, there exist
an unique mixed state~$\rho$ such that $\mu=\tilde{\mu}_{\rho}$.\end{cor}

@@

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(E)=\begin{cases}
1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
\tilde{\mu}_{\ket{0}}(E) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a probability measure. Because $\mu$ is almost
the same as a probability measure~$\tilde{\mu}_{\ket{0}}$, we only
need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\tilde{\mu}_{\rho}(E)=1$ if and only if $\rho$ represents
a pure state and $\rho=E$. \qed\end{example}

@@

Similar to the classical case, by applying the law of large number,
quantum probabilities can be estimated by relative frequencies. For
example, if we want to know the probability of the spin up in the
Stern-Gerlach experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003},
we can put a beam of silver atoms in a highly inhomogeneous magnetic
field, and counting the number of atoms deflects up. Ideally, if the
local field strength directs to the $z$-axis, and all particles have
the same velocity, the Stern-Gerlach experiment only produces two
spots corresponding to $\ket{0}$ and $\ket{1}$. In reality, we need
a lot of resource to keep the local field of strength directing to
the $z$-axis, to keep the atoms having almost the same velocity,
and to point out the exact position each particle landed on.

>>>>

\begin{definition}[Quantum Probability
Space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010}]\label{def:QuantumProbabilitySpace}
  Given a Hilbert space $\Hilb$, a \emph{quantum probability space}
  consists of a set of events $\events$ and a probability measure
  $\tensor*[_{[0,1]}]{\mu}{} : \events \rightarrow [0,1]$ such
  that:\footnote {It is possible to define a more general space of events consisting of
    all operators~$\mathcal{A}$ on $\Hilb$ and consider
    $\mu:\mathcal{A}\rightarrow\C$~\cite{Maassen2010,Swart2013}.  When
    an operator $A\in\mathcal{A}$ is Hermitian, $\mu\left(A\right)$ is
    the expectation value of $A$. We does not take this approach
    because we want to focus only on probability. }
\begin{itemize}
\item $\tensor*[_{[0,1]}]{\mu}{}(\mathbb{1})=1$, and 
\item for mutually orthogonal projections $P_{i}$, we have 
$\tensor*[_{[0,1]}]{\mu}{}\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\tensor*[_{[0,1]}]{\mu}{}\left(P_{i}\right)$.
\end{itemize}
Notice that the preposing $[0,1]$ indicates the range of
$\tensor*[_{[0,1]}]{\mu}{}$. We will only prepose the range of a
probability measure whenever we need to compare the ranges of different
probability measures. 
\qed\end{definition}

@@

\begin{lemma}\label{lem:quantumProbabilityMeasure}Given a Hilbert
space $\Hilb$, a function~$\mu:\events\rightarrow[0,1]$ is a quantum probability
measure if and only if $\mu$ satisfies the following conditions:
\begin{itemize}
\item $\mu(\mathbb{0})=0$, 
\item $\mu(\mathbb{1})=1$, 
\item for any projection $P$,
$\mu\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}P\right)=1\tensor*[_{\mathbb{R}}]{-}{}\mu\left(P\right)$, and 
\item for a set of mutually orthogonal projections $P_{i}$, we have
$\mu\left(\tensor*[_{\mathscr{O}}]{\sum}{_{i}}P_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i}}\mu\left(P_{i}\right)$.
\end{itemize}
\qed\end{lemma}

@@

\begin{cor}\label{cor:Gleason's}Given a Hilbert space $\Hilb$,
for any function~$\mu:\events\rightarrow[0,1]$ satisfying the conditions
listed in lemma~\ref{lem:quantumProbabilityMeasure}, there exist
an unique mixed state~$\rho$ such that $\mu=\tilde{\mu}_{\rho}$.\end{cor}

@@

\begin{example}[One-qubit quantum probability measure] Consider
a quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(E)=\begin{cases}
1 & \textrm{, if }E=\proj{\ps}\textrm{ ;}\\
0 & \textrm{, if }E=\proj{\ms}\textrm{ ;}\\
\tilde{\mu}_{\ket{0}}(E) & \textrm{, otherwise.}
\end{cases}
\]
On one hand, $\mu$ is a quantum probability measure. Because $\mu$ is almost
the same as a quantum probability measure~$\tilde{\mu}_{\ket{0}}$, we only
need to check the orthogonal pair~$\proj{\ps}$ and $\proj{\ms}$:
\[
\mu(\proj{\ps})+\mu(\proj{\ms})=1+0=1\textrm{ .}
\]
On the other hand, $\mu$ cannot be induced by any mixed state because
\[
\mu(\proj{\ps})=\mu(\proj{0})=1\textrm{ .}
\]
However, $\tilde{\mu}_{\rho}(E)=1$ if and only if $\rho$ represents
a pure state and $\rho=E$. \qed\end{example}

@@

Similar to the classical case, by applying the law of large number,
quantum probabilities can be estimated by relative frequencies. For
example, if we want to know the probability of the spin up in the
Stern-Gerlach experiment~\cite{Stern1988,peres1995quantum,544199,Griffiths2003},
we can put a beam of silver atoms in a highly inhomogeneous magnetic
field, and counting the number of atoms deflects up. Ideally, if the
local field strength directs to the $z$-axis, and all particles have
the same velocity, the Stern-Gerlach experiment only produces two
spots corresponding to $\ket{0}$ and $\ket{1}$. In reality, we need
a lot of resource to keep the local field of strength directing to
the $z$-axis precisely, to keep the atoms having almost the same velocity,
and to point out the exact position each particle landed on.
